Adopting agile in the large: motivations, success factors and challenges

### 2013-01-25 tex/article.tex
Introduction: remove talk on plan-driven, and replace with problems in large scale.

As the competition in software industry is growing companies are constantly
looking to improve their effectiveness. Agile methods are claimed to increase
productivity and quality \citegen{Livermore2008}, which makes them attractive for
companies pursuing better performance. However, large organizations may have
problems introducing agile methods \citegen{Dyba2009}. As agile methods are
initially designed for small teams their application has proven to be
problematic in a larger scale \citegen{Boehm2005}.

It is typical for large companies to function according to plan-driven software
engineering models. These models strive for consistent quality and performance
by rigorous planning and definition of process. This kind of approach is however
badly suited for software development, as projects typically encounter
situations that are too hard or impossible to foretell \citegen{Schwaber2002}.
The main problems in plan-driven development are the high cost of changes and
late feedback on quality \citegen{Petersen2010}. Long release cycles, cost of
responding to change and distance from customers undermine the  competitiveness
of companies. Agile methods are believed to bring remedy to these problems.

@@

The literature review was conducted as an application of Kitchenham's
method for systematic literature review (SLR) \citegen{Kitchenham2007}. The method
was applied to be performed by only one researcher, and to serve as a
preliminary work evaluating the feasibility of a more in-depth review.
Effort was limited by selecting only the following subset of SLR steps:
identification of primary sources, data extraction and synthesis. Steps left out
were the development of a systematic review protocol, strict study quality
assessment, and reviews in the study selection process.

The searches for primary sources was conducted in two steps. First a preliminary
search was made to sample the existing literature. Then a systematic search was
done based on the preliminary search. The following databases were included in
the searches: IEEExplore (http://ieeexplore.ieee.org/),
ACM (http://dl.acm.org/), Scopus (http://www.scopus.com/),
ProQuest \linebreak (http://search.proquest.com/).
Additionally the archive of International XP
Conference (http://link.springer.com/) was searched.

@@

The selection process of the primary studies is summarized in Figure
\ref{fig:selection_process}. The database search yielded 1603 matches which were
filtered down to 31 selected primary studies. One study was not available, which
reduced the final number of primary studies to 30.
The 30 primary sources were selected by four criteria: study type, size of
organization, use of agile methods in software development, and a transformation
viewpoint. Firstly, only case studies and experience reports on agile software
development were included in this study. Papers discussing agile methods or
organizational transformation on as a general topic were left out. Secondly, the
size of the organization described in the included primary studies was to be
large enough to show the challenges of large scale agile development
\citegen{Lindvall2004}. Further, only studies discussing agile software
development were included, leaving out for instance studies on agile management.
Finally, the included studies had to provide a viewpoint on the adoption of
agile methods.

>>>>

As the competition in software industry is growing companies are constantly
looking to improve their effectiveness. Agile methods are claimed to increase
productivity and quality \citegen{Livermore2008}, which makes them attractive
for companies pursuing better performance. Agile methods give advantage by
enabling shorter lead times and stronger focus on customer needs
\citegen{Petersen2010}.

However, large organizations may have problems introducing agile methods
\citegen{Dyba2009}. As agile methods are initially designed for small teams
their application has proven to be problematic in a larger scale
\citegen{Boehm2005}. In a large organization development teams will need to
interface with other organizational units. As agile methods tend to focus on
inter-team practices which leaves it up to the organization to figure out how to
make agile work \citegen{Lindvall2004}.

% --> There is demand for a summarizing study of large agile transformations as
% the evidence is currently scattered.
% 
% These models strive for consistent quality and performance
% by rigorous planning and definition of process. This kind of approach is however
% badly suited for software development, as projects typically encounter
% situations that are too hard or impossible to foretell \citegen{Schwaber2002}.
% The main problems in plan-driven development are the high cost of changes and
% late feedback on quality \citegen{Petersen2010}. Long release cycles, cost of
% responding to change and distance from customers undermine the  competitiveness
% of companies. Agile methods are believed to bring remedy to these problems.

@@

The literature review was conducted as an application of Kitchenham's
method for systematic literature review (SLR) \citegen{Kitchenham2007}. The method
was applied to be performed by only one researcher, and to serve as a
preliminary work evaluating the feasibility of a more in-depth review.
Effort was limited by selecting only the following subset of SLR steps:
identification of primary studies, data extraction and synthesis. Steps left out
were the development of a systematic review protocol, strict study quality
assessment, and reviews in the study selection process.

The searches for primary studies was conducted in two steps. First a preliminary
search was made to sample the existing literature. Then a systematic search was
done based on the preliminary search. The following databases were included in
the searches: IEEExplore (http://ieeexplore.ieee.org/),
ACM (http://dl.acm.org/), Scopus (http://www.scopus.com/),
ProQuest \linebreak (http://search.proquest.com/).
Additionally the archive of International XP
Conference (http://link.springer.com/) was searched.

@@

The selection process of the primary studies is summarized in Figure
\ref{fig:selection_process}. The database search yielded 1603 matches which were
filtered down to 31 selected primary studies. One study was not available, which
reduced the final number of primary studies to 30.
The primary studies were selected by four criteria: study type, size of
organization, use of agile methods in software development, and a transformation
viewpoint. Firstly, only case studies and experience reports on agile software
development were included in this study. Papers discussing agile methods or
organizational transformation on as a general topic were left out. Secondly, the
size of the organization described in the included primary studies was to be
large enough to show the challenges of large scale agile development
\citegen{Lindvall2004}. Further, only studies discussing agile software
development were included, leaving out for instance studies on agile management.
Finally, the included studies had to provide a viewpoint on the adoption of
agile methods.
